Racets: Embedding Policy{-}Agnostic Programming in Racket

### 2018-07-20 paper/paper.tex
will add more prose to sec3 later tonight

Faceted execution propagates facets by extending core linguistic
primitives (such as function application). For example, consider the
application \code{(not x)} where \code{x} is
\blue{\facet{Alice}{\code{#t}}{\code{#f}}}. The programmer intends the
call to \code{not} to be operating on a \code{boolean?}, but because
\code{x} is a facet this call produces \code{#f} instead. The correct
way to interpret function application on facets is to distribute the
application through each branch, producing %% \code{m
  %% \mc{ \facet{Alice}{\code{#f}}{\code{not #t}}}}
. Other core forms
(such as \code{if}, \code{cond}, etc...) require similar changes.

The core linguistic changes required by faceted execution have led to
relatively inelegant and heavyweight implementations thusfar. For
example, Flanagan et. al (who first presented faceted execution)
extended the JavaScript runtime to account for faceted
values. Similarly, the Jeeves programming language does (what does it
do?). By contrast, Racket's highly-expressive macro system allows even
core forms (such as \code{#\%app}) to be redefined with relative ease.

@@

We now present a semantics for a core language (\lang) which includes
facets. Our presentation largely mirrors that of Austin et
al.~\cite{Austin:2013}. The syntax of our language---reminiscent of
Scheme---is shown in Figure~\ref{fig:syntax}. \lang extends the lambda
calculus with references (which have interact with facets in a subtle
way) and three forms unique to faceted execution: label creation,
facet construction, and facet observation.

>>>>

Faceted execution propagates facets by extending core linguistic
primitives (such as function application). For example, consider the
application \code{(not x)} where \code{x} is
\blue{\facet{Alice}{\code{#t}}{\code{#f}}}. The programmer intends the
call to \code{not} to be operating on a \code{boolean?}, but because
\code{x} is a facet this call produces \code{#f} instead. The correct
way to interpret function application on facets is to distribute the
application through each branch, producing \zw{producing ...?} %% \code{m
  %% \mc{ \facet{Alice}{\code{#f}}{\code{not #t}}}}
. Other core forms
(such as \code{if}, \code{cond}, etc...) require similar changes.

The core linguistic changes required by faceted execution have led to
relatively inelegant and heavyweight implementations thusfar. For
example, Flanagan et. al (who first presented faceted execution)
extended the JavaScript runtime to account for faceted
values. Similarly, the Jeeves programming language does (what does it
do?)\zw{Need to complete this sentence}. By contrast, Racket's 
highly-expressive macro system allows even
core forms (such as \code{#\%app}) to be redefined with relative ease.

@@

We now present a semantics for a core language (\lang) which includes
facets. Our presentation largely mirrors that of Austin et
al.~\cite{Austin:2013}. The syntax of our language---reminiscent of
Scheme---is shown in Figure~\ref{fig:syntax}. \lang extends the lambda
calculus with references (which have interact with facets in a subtle
way) and three forms unique to faceted execution: facet construction, 
label creation, and facet observation.

\zw{Facet construction allows the users to construct a facet value that
consists of a policy, a private/positive variable that can be a basic value
or another facet value but is hidden away from other users, and a public/negative 
variable. }

\zw{Label creation dynamically creates a label binding to a given policy.
A policy consists of a policy variable and a policy body/expression. 
When a lable is invoked in the faceted executions, the policy will be called
to evaluate the given faceted value. When the policy is invoked, the policy
body (e.g. lambda function) evaluates to a boolean, which indicates whether
to observe the positive or the negative branch of a faceted value. This allows
the users to protect their data via choosing what data to be seen by others and 
hiding the sensitive data.}

\zw{Facet observation }
